Supervised Dimensionality Reduction with Random Projection-Based Ensemble Learning

### 2021-03-29 paper/main.tex

%\setlength{\parindent}{.3in}
%\setlength{\parskip}{.05in}
\usepackage{natbib}
\usepackage{latexsym,amsmath,amssymb,amsfonts,amsthm,bbm,mathrsfs,breakcites, dsfont,xcolor}
\usepackage{stmaryrd,epsf}
\usepackage{soul}
\usepackage{url}
\usepackage{dsfont}
\usepackage{enumerate}
\usepackage{enumitem}   
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{psfrag}
\usepackage{caption, subcaption}
%\usepackage{algorithm}
\usepackage[ruled,vlined]{algorithm2e}

@@

We present two simulation studies, of distributions with known central subspaces, and compare our method with other techniques for supervised dimension reduction. \\
~\\
\textbf{Sparse class boundaries}\\
First, we let 
\[X \ | \ \{Y = 0\} \sim \frac{1}{2}N_p(\mu_0, \Sigma) + \frac{1}{2}N_p(-\mu_0, \Sigma) \]
\[X \ | \ \{ Y = 1\} \sim \frac{1}{2}N_p(\mu_1, \Sigma) + \frac{1}{2}N_p(-\mu_1, \Sigma). \]
We set $p=100$, $\mu_0 = (1/\sqrt{2}, -1/\sqrt{2}, 0, \ldots, 0)^T$, $\mu_1 = (1/\sqrt{2}, 1/\sqrt{2}, 0, \ldots, 0)^T$ and let $\Sigma$ be a diagonal with $\Sigma_{11} = \Sigma_{22} = 1/\sqrt{2}$ and $\Sigma_{jj} = 1$ for $j>2$. This model exhibits a setup in which a central subspace exists (of dimension $d^* = 2)$, but there is no good linear class boundary and the dimensions of interest are not necessarily the dimensions of greatest variance. \\
~\\

>>>>

%\setlength{\parindent}{.3in}
%\setlength{\parskip}{.05in}
\usepackage{natbib}
\usepackage{latexsym,amsmath,amssymb,amsfonts,amsthm,bbm,mathrsfs,breakcites, dsfont,xcolor}
\usepackage{stmaryrd,epsf}
\usepackage{soul}
\usepackage{url}
\usepackage{dsfont}
\usepackage{enumerate}
\usepackage{enumitem}   
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{psfrag}
\usepackage{caption, subcaption}
\usepackage{booktabs}
%\usepackage{algorithm}
\usepackage[ruled,vlined]{algorithm2e}

@@

We present two simulation studies, of distributions with known central subspaces, and compare our method with other techniques for supervised dimension reduction. \\
~\\
\textbf{Sparse class boundaries}\\
First, we let 
\[X \ | \ \{Y = 0\} \sim \frac{1}{2}N_p(\mu_0, \Sigma) + \frac{1}{2}N_p(-\mu_0, \Sigma) \]
\[X \ | \ \{ Y = 1\} \sim \frac{1}{2}N_p(\mu_1, \Sigma) + \frac{1}{2}N_p(-\mu_1, \Sigma). \]
We set $p=100$, $\mu_0 = (2, -2, 0, \ldots, 0)^T$, $\mu_1 = (2, 2, 0, \ldots, 0)^T$ and let $\Sigma = I_{100}$. This model exhibits a setup in which a central subspace exists (of dimension $d^* = 2)$, but there is no good linear class boundary. \\
~\\

\begin{table}
  \caption{Simulation performance}
  \label{sample-table}
  \centering
  \begin{tabular}{l|lll|lll}
    \toprule
    \multicolumn{2}{c}{Model 1} & \multicolumn{2}{c}{Model 2}                     \\
    \cmidrule(r){1-4}
    Method     & Power     & False & Accuracy &  Power     & False & Accuracy &  \\
    & & Discovery & & & Discovery &
    \midrule
    RP-LDA & Input terminal  & $\sim$100  &  &&& \\
    RP-QDA    & Output terminal & $\sim$10    &  &&&\\
    RP-kNN     & Cell body       & up to $10^6$ & &&& \\
    \bottomrule
  \end{tabular}
\end{table}

% First, we let 
% \[X \ | \ \{Y = 0\} \sim \frac{1}{2}N_p(\mu_0, \Sigma) + \frac{1}{2}N_p(-\mu_0, \Sigma) \]
% \[X \ | \ \{ Y = 1\} \sim \frac{1}{2}N_p(\mu_1, \Sigma) + \frac{1}{2}N_p(-\mu_1, \Sigma). \]
% We set $p=100$, $\mu_0 = (1/\sqrt{2}, -1/\sqrt{2}, 0, \ldots, 0)^T$, $\mu_1 = (1/\sqrt{2}, 1/\sqrt{2}, 0, \ldots, 0)^T$ and let $\Sigma$ be a diagonal with $\Sigma_{11} = \Sigma_{22} = 1/\sqrt{2}$ and $\Sigma_{jj} = 1$ for $j>2$. This model exhibits a setup in which a central subspace exists (of dimension $d^* = 2)$, but there is no good linear class boundary and the dimensions of interest are not necessarily the dimensions of greatest variance. \\
% ~\\
